Automated Synthesis of State-Space Digital Systems

### 2016-12-21 cav2017/cav2017.tex
review Preliminaries

%-------------------------------
\section{Preliminaries}
%-------------------------------
In this work we will focus on Linear Dynamical Cyberphisical Systems with
continuous plants described by ODEs in the form
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\\
\vec{y}(t)&=\mat{C}\vec{x}+\mat{D}\vec{u}\nonumber
\end{align}
which are soundly discretized (as shown in the appendix) into 
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k\nonumber
\end{align}
and Digital Controllers in the form
\begin{equation}
\vec{u}_k=\mat{K}_d\vec{y}_k
\end{equation}
The output of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed).

We further presume that there are small tolerances in the system described in the
following form
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\mat{B} \in \mathcal{G}_B
\end{align*}

Finally, we also require a safety specification $\Psi(\vec{u},\vec{y})$ which is
given as a set of linear constraints over the inputs and outputs.

>>>>

%-------------------------------
\section{Preliminaries}
%-------------------------------
In this study, we focus on Linear Dynamical Cyber-Physical Systems with
continuous plants described by Ordinary Differential Equations (ODEs) 
in the form
%
\begin{align}
\label{eq:ode}
\dot{\vec{x}}(t)&=\mat{A}\vec{x}(t)+\mat{B}\vec{u}(t)\\
\vec{y}(t)&=\mat{C}\vec{x}+\mat{D}\vec{u},\nonumber
\end{align}
which are soundly discretized (as shown in the appendix) into 
\begin{align}
\label{eq:plant}
\vec{x}_{k+1}&=\mat{A}_d\vec{x}_k+\mat{B}_d\vec{u}_k\\
\vec{y}_k&=\mat{C}_d\vec{x}_k+\mat{D}_d\vec{u}_k,\nonumber
\end{align}
%
and digital controllers in the form
%
\begin{equation}
\vec{u}_k=\mat{K}_d\vec{y}_k.
\end{equation}
%
The output of the plant is being sampled by an ADC, and since the full state of the
plant cannot be witnessed directly, the controller software includes an observer that 
estimates the state of the plant (see appendix for details on how such an observer
is constructed). We further presume that there are small tolerances in the system 
described in the following form
%
\begin{align*}
\mat{A} \in \mathcal{G}_A=\mat{S}\mat{J}\mat{S}^{-1} : \mat{J} \in \mathcal{G}_J
\mat{B} \in \mathcal{G}_B.
\end{align*}

Finally, we also require a safety specification $\Psi(\vec{u},\vec{y})$, which is
given as a set of linear constraints over the inputs and outputs.
